---
output: html_document
editor_options: 
  chunk_output_type: console
---
Lesson 3
========================================================

***

### What to Do First?
Notes:

***

### Pseudo-Facebook User Data
Notes:

```{r}
getwd()
pf <- read.csv('pseudo_facebook.tsv', sep = '\t')
names(pf)
```

***

### Histogram of Users' Birthdays
Notes:
```{r Histogram of Users\' Birthdays and the idea behind scale_x}
library(ggplot2)
# scaling is just divide our x axis into breaks from start to end.
qplot(x=dob_day , data = pf ) + scale_x_continuous(breaks=1:31)
```

***

### Faceting
Facetinng is about splitting histograms 

```{r Faceting}

qplot(x=dob_day , data = pf ) + 
  scale_x_continuous(breaks=1:31) +
  facet_wrap(~dob_month,ncol=4)
```

***
#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}
qplot(x=friend_count , data = pf )
```

#### How is this plot similar to Moira's first plot?
Response:

***

### Limiting the Axes
Notes:

```{r Limiting the Axes}
# Limiting the Axis is just limit your axis between start and end points that you choose not set by default as from data .
qplot(x=friend_count , data = pf )+
  scale_x_continuous(limits = c(0,1000))
```

### Exploring with Bin Width
Notes:

***
### Adjusting the Bin Width
```{r Adjusting the Bin Width}
qplot(x = friend_count, data = pf, binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))
```

*** 
### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.
qplot(x = friend_count, data = pf, binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))+
  facet_wrap(~gender)
```

***

### Omitting Null Values that are in gender variable.
```{r Omitting NA Values}
qplot(x = friend_count, data = subset(pf , !is.na(gender)), binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))+
  facet_wrap(~gender)
```

***

### Statistics 'by' Gender
Notes:


```{r taking the summary of one of the varaibles}
summary(pf$gender)
```


```{r Statistics \'by\' Gender, Summerizing the data by another variable}
table(pf$gender)
by(pf$friend_count,pf$gender,summary)
```

***

### Tenure
Notes:

```{r Tenure}
qplot(x=tenure,data=pf,  binwidth = 30,
      color =I('black'),fill=I('#099DD9'))
```

***

#### Labeling axis.

```{r Tenure Histogram by Year }
# a very nice histogram with namming the x-axis and y-axis. 
qplot(x = tenure/365 , data = pf ,
      binwidth = .25,
      xlab = 'Tenure',
      ylab = 'Count',
      color = I('black'), fill = I('#099DD9'))+
  scale_x_continuous(breaks = seq(1,7,1) , lim = c(0,7))
```

***

### User Ages
Notes:

```{r User Ages}
qplot(x = age , data = pf , binwidth = 1,
      xlab = 'Age of users on Facebook' ,
      ylab = 'Count',
      color = I('Red'), fill = I('#099DD9'))+
  scale_x_continuous(breaks=seq(0,113,5))
```
*** 

### Transforming Data
Notes:
I think that it is important since it will help in avoiding have a very long tail and will decrease the x-axis values.!

***
### Creating Mulitple histograms

```{r Transforming Data}
#install.packages('gridExtra')
#library(gridExtra)
p1 <- qplot(x=friend_count, data=pf)
p2 <- qplot(x=log10(friend_count +1), data=pf)
p3 <- qplot(x=sqrt(friend_count) , data=pf)


grid.arrange(p1,p2,p3,ncol = 1)
```


### Printing multiple histograms in one image.
```{r Transforming Data Using ggplot}
p1 <- ggplot(aes(x=friend_count),data=pf) + geom_histogram()
p2 <- p1+scale_x_log10()
p3 <- p1+scale_x_sqrt()

grid.arrange(p1,p2,p3,ncol = 1)
```

### Notes:
It is better to have a normal distribuation since linear regression better fit in it .


***

### Printing out the difference between scale_x_log10 and log10 (wrapper)
```{r Add a Scaling Layer}
logScale <- qplot(x=log10(friend_count) , data=pf)
countScale <- ggplot(aes(x=friend_count),data=pf) +
  geom_histogram() +
  scale_x_log10()

grid.arrange(logScale,countScale,ncol =2 )
```

***

### Frequency Polygons

```{r Frequency Polygons}
qplot(x=friend_count, y = ..count../sum(..count..),
      data = subset(pf,!is.na(gender)),
      xlab= 'Friend_count',
      ylab= 'Probability of User with friend_count',
      binwidth=10, geom ='freqpoly',color=gender)+
  scale_x_continuous(lim = c(0,1000),breaks=seq(0,1000,50))

```

***

### Likes on the Web
Notes:

```{r Likes on the Web}
qplot(x=www_likes,
      data = subset(pf,!is.na(www_likes)),
      xlab= 'www-likes',
      ylab= 'Probability of User with likes',
      geom ='freqpoly',color=gender)+
      scale_x_continuous()+
      scale_x_log10()
```

```{r Who get the most likes, Female or Male ?? }
by(pf$www_likes,pf$gender,sum)
```

***

### Box Plots
Notes:

```{r Box Plots}

```

#### Adjust the code to focus on users who have friend counts between 0 and 1000.

```{r}

```

***

### Box Plots, Quartiles, and Friendships
Notes:

```{r Box Plots, Quartiles, and Friendships}

```

#### On average, who initiated more friendships in our sample: men or women?
Response:
#### Write about some ways that you can verify your answer.
Response:
```{r Friend Requests by Gender}

```

Response:

***

### Getting Logical
Notes:

```{r Getting Logical}

```

Response:

***

### Analyzing One Variable
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!